### 2016-07-25 ms/ms.tex
added cv occurence

\section*{Introduction}
\label{sec:introduction}
\begin{itemize}
\item The structure of networks is related to ability of communities
  to maintain function in the face of species extinction.
\item A key restoration aim is to facilitate assembly of robust
  networks; thus it is critical to study how restoration
  influences the assembly of plant-pollinator interactions.
\item few theories about how networks assemble, preferential
  attachment 
\item To date, only two field studies have examined how networks
  assemble over time, often using space for time gradients.
\item \cite{Olesen2008} was investigated day-to-day, temporal assmebly
  of a plant-pollinator network within a season, taking advantage of
  the extreme seasonality of pollinator communities in Greenland.
  \cite{Olesen2008} found that within a season, the network assembly
  was similar to preferential attachment. New species tended to
  interact predominantly with already well-connected species, likely
  because these species are either more abundant or more temporally
  persistent.
\item Studying primary succession along a glacier foreland,
  \cite{albrecht2010plant} found a similar pattern where nestedness, a
  pattern of interactions where a generalist core interacts with both
  specialist and generalist species, increased as the community
  aged. % Studying ``managed succession'' of a clear-cut pine forest,
  % \cite{devoto2012understanding} found changes in network structure
  % were explained by a combination of age, tree density and variation
  % in tree diameter. 
\item Even non-succesional temporal dyanmics suggest a stable core of
  generalsits persiss despite high turnover of peripheral species
  \citep{fang2012relative, diaz2010changes, alarcon2008year}.
\item In contrast to the ordered notion of netowrk build-up described
  by perferential attachment, assembly may be punctated by significant
  reorganizations of interactions. For example, as new species are
  added, resident species may change their interaction parteners to
  minimize competition, or go extinct if they are unable to persist
  with more competing species.
\end{itemize}

@@

We would like to thank Leto Peel and Aaron Clauset for their
invaluable discussions and for help with the change point analysis.
We thank the growers and land owners that allowed us to work on their
property.  We also appreciate the identification assistance of expert
taxonomists Robbin Thorp and Jason Gibbs.  This work was supported by
funding from the Army Research Office (W911NF-11-1-0361 to CK), the
Natural Resources Conservation Service (CIG-69-3A75-12-253,
CIG-69-3A75-9-142, CIG-68-9104-6-101 and WLF-69-7482-6-277 to The
Xerces Society), the National Science Foundation (DEB-0919128 to CK),
The U.S.  Department of Agriculture (USDA-NIFA 2012-51181-20105 to
Michigan State University).  Funding for LCP was provided by an NSF
Graduate Research Fellowship and the USDA NIFA Graduate
Fellowship. FUNING FOR MARILLIA.

>>>>

\section*{Introduction}
\label{sec:introduction}
\begin{itemize}
\item The structure of networks is related to ability of communities
  to maintain function in the face of species extinction.
\item A key restoration aim is to facilitate assembly of robust
  networks; thus it is critical to study how restoration
  influences the assembly of plant-pollinator interactions.
\item few theories about how networks assemble, preferential
  attachment 
\item To date, only two field studies have examined how networks
  assemble over time, often using space for time gradients.
\item \cite{Olesen2008} was investigated day-to-day, temporal assmebly
  of a plant-pollinator network within a season, taking advantage of
  the extreme seasonality of pollinator communities in Greenland.
  \cite{Olesen2008} found that within a season, the network assembly
  was similar to preferential attachment. New species tended to
  interact with already well-connected species, likely because these
  species are either more abundant or more temporally persistent.
\item Studying primary succession along a glacier foreland,
  \cite{albrecht2010plant} found a similar pattern where nestedness, a
  pattern of interactions where a generalist core interacts with both
  specialist and generalist species, increased as the community
  aged. % Studying ``managed succession'' of a clear-cut pine forest,
  % \cite{devoto2012understanding} found changes in network structure
  % were explained by a combination of age, tree density and variation
  % in tree diameter. 
\item Even non-succesional temporal dyanmics suggest a stable core of
  generalsits persiss despite high turnover of peripheral species
  \citep{fang2012relative, diaz2010changes, alarcon2008year}.
\item In contrast to the ordered netowrk build-up described by
  perferential attachment, assembly may be punctated by significant
  reorganizations of interactions. For example, as new species are
  added, resident species change their interaction parteners to
  minimize competition, or become extinct.
\end{itemize}

@@

We would like to thank Leto Peel and Aaron Clauset for their
invaluable discussions and for help with the change point analysis.
We thank the growers and land owners that allowed us to work on their
property.  We also appreciate the identification assistance of expert
taxonomists Martin Hauser, Robbin Thorp and Jason Gibbs.  This work
was supported by funding from the Army Research Office
(W911NF-11-1-0361 to CK), the Natural Resources Conservation Service
(CIG-69-3A75-12-253, CIG-69-3A75-9-142, CIG-68-9104-6-101 and
WLF-69-7482-6-277 to The Xerces Society), the National Science
Foundation (DEB-0919128 to CK), The U.S.  Department of Agriculture
(USDA-NIFA 2012-51181-20105 to Michigan State University).  Funding
for LCP was provided by an NSF Graduate Research Fellowship and the
USDA NIFA Graduate Fellowship. FUNING FOR MARILLIA.
